### 2013-09-26 Tex/chapters/results.tex
power law fit benutzt zur K-normalisierung

@@

                degree. There seems to be an in first approximation linear
                dependency. But at \(K \approx 4\) the jump also seen in
                Fig.\ \ref{fig:Tc} occurs. Also slight curvature can be
                recognized and is further examined in Fig.\ \ref{fig:Tc_deg}.

@@

        but is still existent. Anyway, the degree seems to have an impact on

@@

            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg}
            }
            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg}
            }

            \caption[Critical Temperature Normalized by Degree of the Graph]
            {
                Top: Degree \(K\) of graph over different
                disorder parameters \(\sigma\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Bottom: Critical temperatures normalized by degree over different
                disorder parameters for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG.
            }
            \label{fig:Tc_deg}
        \end{figure}\\
        To understand the jump of \(T_c\) it seems to be necessary to
        understand the jump of \(K\), which is easily explained
        by the definition of the GG. As evident from Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
        a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
        To fully understand this, take four nodes forming a square. The edge
        across the diagonal of the plaquette does not exist, because the
        other two nodes are located exactly on the border
        of the lune. Moving one node slightly into the square, causes the lune
        to get smaller, hence no other nodes are inside or on the border of
        the lune anymore and the new diagonal edge appears. This process is sketched in
        Fig.\ \ref{fig:GGEdge}.
        \begin{figure}[htb]
            \centering
            \subfigure[][]{
                \label{sfig:GGEdge:before}
                \input{images/GGEdgeBefore}
            }
            \subfigure[][]{
                \label{sfig:GGEdge:after}
                \input{images/GGEdgeAfter}
            }
            \caption[Sketch why Many New Edges Arise at the Transition from $\sigma = 0$ to $\sigma > 0$]
            {
                \subref{sfig:GGEdge:before} The edge across does not exist,
                because the other two nodes are on the edge of the lune.
                \subref{sfig:GGEdge:after} Moving one node slightly into the
                square, causes the lune to get smaller, hence no other nodes
                are inside or on the edge of the lune anymore and the edge
                appears.
            }
            \label{fig:GGEdge}
        \end{figure}\\
        Further, the increase of \(T_c\) on the GG can be made plausible.
        Also, the maximum value of \(K\) and the maximum value of \(T_c\)
        are observed at a similar value of \(\sigma\). Hence, while displacing the nodes, there arise more edges
        than edges are vanishing until \(\sigma \approx 0.15\) is reached.
        Then more edges disappear than appear at further displacement. This
        is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}.
        \begin{figure}[htb]
            \subfigure[][$\sigma = 0.00$]
            {
                \label{sfig:GG_sigma:0.00}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
            }
            \subfigure[][$\sigma = 0.01$]
            {
                \label{sfig:GG_sigma:0.01}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
            }

>>>>

        In fact one can fit

@@

                degree. At \(K \approx 4\) the jump also seen in Fig.\ \ref{fig:Tc} occurs.
                There seems to be an in first approximation linear
                dependency. The dotted lines are fits to a power law function \(T_c = aK^b\)
                ignoring the point at \(K=4\) on the GG.
                As a approximation it seems suited but besides the bad
                \(\chi^2\) values are hints that there is some finer
                structure which is not fitted by a power law function.
                This is further examined in Fig.\ \ref{fig:Tc_deg}.

@@

        but is still existent.\\
        In Fig.\ \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg_fit:RNG}\subref{sfig:Tc_norm_deg_fit:GG}
        the normalization is done using the found power law function.
        The amplitude of the curve shrinks which is a hint, that this is a good
        approximation. But it is not a constant, so there have to be other
        influences.
        Anyway, the degree seems to have a major impact on

@@

            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg}
            }
            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg}
            }
            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg_fit:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_fit}
            }
            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg_fit:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_fit}
            }

            \caption[Critical Temperature Normalized by Degree of the Graph]
            {
                Top: Degree \(K\) of graph over different
                disorder parameters \(\sigma\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Middle: Critical temperatures normalized by degree over different
                disorder parameters for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG.
                Bottom: Critical temperatures normalized by the in Fig.\ \ref{fig:Tc_K}
                determined power law function over different
                disorder parameters for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG.
                Note that the \(\sigma = 0\) point of the GG is not displayed.
                The found power law function seems to be a good approximation.
                But at least for the RNG and at least for small values of
                \(\sigma\) on the GG it can not explain everything.
            }
            \label{fig:Tc_deg}
        \end{figure}\\
        To understand the jump of \(T_c\) it seems to be necessary to
        understand the jump of \(K\), which is easily explained
        by the definition of the GG. As evident from Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
        a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
        To fully understand this, take four nodes forming a square. The edge
        across the diagonal of the plaquette does not exist, because the
        other two nodes are located exactly on the border
        of the lune. Moving one node slightly into the square, causes the lune
        to get smaller, hence no other nodes are inside or on the border of
        the lune anymore and the new diagonal edge appears. This process is sketched in
        Fig.\ \ref{fig:GGEdge}.
        \begin{figure}[htb]
            \centering
            \subfigure[][]{
                \label{sfig:GGEdge:before}
                \input{images/GGEdgeBefore}
            }
            \subfigure[][]{
                \label{sfig:GGEdge:after}
                \input{images/GGEdgeAfter}
            }
            \caption[Sketch why Many New Edges Arise at the Transition from $\sigma = 0$ to $\sigma > 0$]
            {
                \subref{sfig:GGEdge:before} The edge across does not exist,
                because the other two nodes are on the edge of the lune.
                \subref{sfig:GGEdge:after} Moving one node slightly into the
                square, causes the lune to get smaller, hence no other nodes
                are inside or on the edge of the lune anymore and the edge
                appears.
            }
            \label{fig:GGEdge}
        \end{figure}\\
        Further, the increase of \(T_c\) on the GG can be made plausible.
        Also, the maximum value of \(K\) and the maximum value of \(T_c\)
        are observed at a similar value of \(\sigma\). Hence, while displacing the nodes, there arise more edges
        than edges are vanishing until \(\sigma \approx 0.15\) is reached.
        Then more edges disappear than appear at further displacement. This
        is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}.
        \begin{figure}[htb]
            \subfigure[][$\sigma = 0.00$]
            {
                \label{sfig:GG_sigma:0.00}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
            }
            \subfigure[][$\sigma = 0.01$]
            {
                \label{sfig:GG_sigma:0.01}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
            }
